\bf An Examination of Sport Climbing Competition Format and Scoring System

### 2021-08-04 manuscript/Rmd/draft.Rmd
Add simulation tables and plots

```{r}
mosaic::favstats(score ~ round, data = qual_final)[-10] %>% 
  kable(caption = "Descriptive statistics of simulated scores for qualification and final rounds",
        booktabs = TRUE,
        position = "H")
```

@@

In this section, we discuss the results of our simulations described in Section \ref{data-and-methods}. For the qualification round, our simulation study shows that a climber is almost guaranteed to make the final round if they win the first event or if they win at least one of the three climbing concentrations  (99.51% and 99.48% change of advancing, respectively). On the other hand, finishing last in the first event or in any event would certainly hurt an athlete's chance of finishing in the top 8, as the probabilities of a climber advancing given they finish last in the first and in any event are 0.1830 and 0.1885, respectively. In addition, the average score for qualification positions 1 to 8 are displayed in Table 2. We notice that on average, the minimum score that one should aim for in order to move on to the final round is about 434 (for 8th rank).

@@

>>>>

```{r}
mosaic::favstats(score ~ round, data = qual_final)[-10] %>% 
  kable(caption = "Descriptive statistics of simulated scores for qualification and final rounds",
        booktabs = TRUE,
        position = "H",
        digits = 2)
```

@@

In this section, we discuss the results of our simulations described in Section \ref{data-and-methods}. We first look at the chances of advancing to the final round for a qualifier, given that 1) they finish first in any of the three disciplines, and 2) they win the first event (which happens to be speed climbing in reality). Our simulation study shows that a climber is almost guaranteed to make the final round if they win at least one of the three climbing concentrations (99.51%, see Table) or if they win the opening event (99.48%, see Table). After winning the first event, a climber is also more likely to finish first overall (30%, see Table) than any other positions in the overall qualification rankings. Therefore, this product of ranks scoring format highly rewards climbers who can get off to a strong start, which is a major strategy climbing athletes should take note of.

In addition, the average score for qualification positions 1 to 8 are displayed in Table X. We notice that on average, the minimum score that one should aim for in order to move on to the final round is about 434 (for 8th rank).

```{r}
win_any_qual <- qual %>% 
  filter(e1 == 1 | e2 == 1 | e3 == 1) %>% 
  count(rank) %>% 
  mutate(prob = n / sum(n),
         cum_prob = cumsum(prob))
win_first_qual <- qual %>% 
  filter(e1 == 1) %>% 
  count(rank) %>% 
  mutate(prob = n / sum(n),
         cum_prob = cumsum(prob))

cbind(win_any_qual, win_first_qual) %>% 
  kable(col.names = rep(c("Rank", "Count", "Probability", "Cumulative"), 2),
        caption = "title", 
        booktabs = TRUE, 
        position = "H",
        digits = 4) %>% 
  add_header_above(c("Win Any" = 4, "Win First" = 4)) %>%
  kable_styling(latex_options = c("repeat_header", "scale_down"))
```

```{r, fig.cap="Probability of finishing at every rank given", fig.width = 6.4, fig.height = 3.2}
win_any_qual %>% 
  mutate(type = "Win Any") %>% 
  bind_rows(mutate(win_first_qual, type = "Win First")) %>% 
  mutate(finalist = ifelse(rank %in% 1:8, "Yes", "No")) %>% 
  ggplot(aes(rank, weight = prob, fill = finalist)) +
  geom_bar() +
  geom_vline(xintercept = 8.5) +
  scale_x_continuous() +
  labs(x = "Rank",
       y = "Probability",
       fill = "Finalist") +
  facet_wrap(~ type)
```

<!--
On the other hand, finishing last in the first event or in any event would certainly hurt an athlete's chance of finishing in the top 8, as the probabilities of a climber advancing given they finish last in the first and in any event are 0.1830 and 0.1885, respectively.
-->

@@

```{r}
win_any_final <- final %>% 
  filter(e1 == 1 | e2 == 1 | e3 == 1) %>% 
  count(rank) %>% 
  mutate(prob = n / sum(n),
         cum_prob = cumsum(prob))
win_first_final <- final %>% 
  filter(e1 == 1) %>% 
  count(rank) %>% 
  mutate(prob = n / sum(n),
         cum_prob = cumsum(prob))

cbind(win_any_final, win_first_final) %>% 
  kable(col.names = rep(c("Rank", "Count", "Probability", "Cumulative"), 2),
        caption = "title", 
        booktabs = TRUE, 
        position = "H",
        digits = 4) %>% 
  add_header_above(c("Win Any" = 4, "Win First" = 4)) %>%
  kable_styling(latex_options = c("repeat_header", "scale_down"))
```

```{r, fig.cap="Probability of finishing at every rank given", fig.width = 6.4, fig.height = 3.2}
win_any_final %>% 
  mutate(type = "Win Any") %>% 
  bind_rows(mutate(win_first_final, type = "Win First")) %>% 
  mutate(medalist = ifelse(rank %in% 1:3, "Yes", "No")) %>% 
  ggplot(aes(rank, weight = prob, fill = medalist)) +
  geom_bar() +
  geom_vline(xintercept = 3.5) +
  scale_x_continuous() +
  labs(x = "Rank",
       y = "Probability",
       fill = "Medalist") +
  facet_wrap(~ type)
```

### 2021-08-04 manuscript/Rmd/draft.tex
Add simulation tables and plots

\caption{\label{tab:unnamed-chunk-4}Descriptive statistics of simulated scores for qualification and final rounds}
\centering
\begin{tabular}[t]{lrrrrrrrr}
\toprule
round & min & Q1 & median & Q3 & max & mean & sd & n\\
\midrule
Qualification & 1 & 240 & 684 & 1638 & 8000 & 1158.84378 & 1273.47884 & 200000\\
Final & 1 & 24 & 60 & 126 & 512 & 91.19935 & 91.11065 & 80000\\
\bottomrule
\end{tabular}
\end{table}

@@

In this section, we discuss the results of our simulations described in
Section \ref{data-and-methods}. For the qualification round, our
simulation study shows that a climber is almost guaranteed to make the
final round if they win the first event or if they win at least one of
the three climbing concentrations (99.51\% and 99.48\% change of
advancing, respectively). On the other hand, finishing last in the first
event or in any event would certainly hurt an athlete's chance of
finishing in the top 8, as the probabilities of a climber advancing
given they finish last in the first and in any event are 0.1830 and
0.1885, respectively. In addition, the average score for qualification
positions 1 to 8 are displayed in Table 2. We notice that on average,
the minimum score that one should aim for in order to move on to the
final round is about 434 (for 8th rank).

@@

\caption{\label{tab:unnamed-chunk-6}The average scores for the top 10 qualification ranks according to our simulations. A climber will secure a finalist spot if they finish in the top 8.}
\centering
\begin{tabular}[t]{rr}
\toprule
Rank & Average score\\
\midrule
1 & 36.0187\\
2 & 73.6111\\
3 & 115.3954\\
4 & 162.2263\\
5 & 216.0041\\
\addlinespace
6 & 278.1649\\
7 & 350.3272\\
8 & 434.5932\\
9 & 532.1383\\
10 & 642.3298\\
\bottomrule
\end{tabular}
\end{table}

@@

@@

\caption{\label{tab:unnamed-chunk-7}The average scores for all final ranks according to our simulations. Ranks 1, 2, and 3 are table positions that guarantee medalist status for climbers.}
\centering
\begin{tabular}[t]{rr}
\toprule
Rank & Average score\\
\midrule
1 & 9.6687\\
2 & 20.1844\\
3 & 33.3658\\
4 & 50.5734\\
5 & 75.2499\\
\addlinespace
6 & 110.7070\\
7 & 164.8258\\
8 & 265.0198\\
\bottomrule
\end{tabular}
\end{table}

@@

{\centering \includegraphics{draft_files/figure-latex/unnamed-chunk-9-1}

@@

\caption{Kendall's rank correlations - 2018 World Championship, Men's and Women's Qualifications}\label{fig:unnamed-chunk-9}
\end{figure}

@@

{\centering \includegraphics{draft_files/figure-latex/unnamed-chunk-12-1}

@@

\caption{This figure illustrates the changes to the final rankings of the 2018 Youth Olympics Men's and Women's Finals when we leave out one climber. For each gender competition, each panel represents the rank of the drop-out athlete, with 0 being the original final results. Each case with a change in rank orderings is highlighted by a black panel border, and any player with a rank change is represented by a red-filled bar}\label{fig:unnamed-chunk-12}
\end{figure}

@@

\caption{\label{tab:unnamed-chunk-14}This table shows Kendall's rank correlation coefficients between the overall and individual discipline ranks for men's and women's sport climbing qualifications at the 2018 Asian Games}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lrrrrrrrr}
\toprule
\multicolumn{1}{c}{} & \multicolumn{4}{c}{Men} & \multicolumn{4}{c}{Women} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9}
  & Overall & Speed & Bouldering & Lead & Overall & Speed & Bouldering & Lead\\
\midrule
Overall & 1.0000 & 0.5731 & 0.6760 & 0.6126 & 1.0000 & 0.5474 & 0.6878 & 0.7053\\
Speed & 0.5731 & 1.0000 & 0.3022 & 0.2174 & 0.5474 & 1.0000 & 0.2540 & 0.2947\\
Bouldering & 0.6760 & 0.3022 & 1.0000 & 0.6203 & 0.6878 & 0.2540 & 1.0000 & 0.6878\\
Lead & 0.6126 & 0.2174 & 0.6203 & 1.0000 & 0.7053 & 0.2947 & 0.6878 & 1.0000\\
\bottomrule
\end{tabular}}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-15}This table shows Kendall's rank correlation coefficients between the overall and individual discipline ranks for men's and women's sport climbing qualifications at the 2019 World Championships}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lrrrrrrrr}
\toprule
\multicolumn{1}{c}{} & \multicolumn{4}{c}{Men} & \multicolumn{4}{c}{Women} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9}
  & Overall & Speed & Bouldering & Lead & Overall & Speed & Bouldering & Lead\\
\midrule
Overall & 1.0000 & 0.2632 & 0.3684 & 0.3474 & 1.0000 & 0.2316 & 0.5013 & 0.2526\\
Speed & 0.2632 & 1.0000 & -0.0947 & -0.3263 & 0.2316 & 1.0000 & 0.0686 & -0.4526\\
Bouldering & 0.3684 & -0.0947 & 1.0000 & 0.2000 & 0.5013 & 0.0686 & 1.0000 & 0.2902\\
Lead & 0.3474 & -0.3263 & 0.2000 & 1.0000 & 0.2526 & -0.4526 & 0.2902 & 1.0000\\
\bottomrule
\end{tabular}}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-16}This table shows Kendall's rank correlation coefficients between the overall and individual discipline ranks for men's and women's sport climbing qualifications at the 2020 European Championship}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lrrrrrrrr}
\toprule
\multicolumn{1}{c}{} & \multicolumn{4}{c}{Men} & \multicolumn{4}{c}{Women} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9}
  & Overall & Speed & Bouldering & Lead & Overall & Speed & Bouldering & Lead\\
\midrule
Overall & 1.0000 & 0.0947 & 0.3810 & 0.2632 & 1.0000 & 0.1847 & 0.5358 & 0.5368\\
Speed & 0.0947 & 1.0000 & -0.1587 & -0.4316 & 0.1847 & 1.0000 & -0.1915 & -0.0897\\
Bouldering & 0.3810 & -0.1587 & 1.0000 & 0.2751 & 0.5358 & -0.1915 & 1.0000 & 0.5040\\
Lead & 0.2632 & -0.4316 & 0.2751 & 1.0000 & 0.5368 & -0.0897 & 0.5040 & 1.0000\\
\bottomrule
\end{tabular}}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-17}This table shows Kendall's rank correlation coefficients between the overall and individual discipline ranks for men's and women's sport climbing qualifications at the 2020 Pan American Championship}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lrrrrrrrr}
\toprule
\multicolumn{1}{c}{} & \multicolumn{4}{c}{Men} & \multicolumn{4}{c}{Women} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9}
  & Overall & Speed & Bouldering & Lead & Overall & Speed & Bouldering & Lead\\
\midrule
Overall & 1.0000 & 0.5906 & 0.5556 & 0.6491 & 1.0000 & 0.5789 & 0.6140 & 0.5906\\
Speed & 0.5906 & 1.0000 & 0.2164 & 0.4035 & 0.5789 & 1.0000 & 0.2632 & 0.3099\\
Bouldering & 0.5556 & 0.2164 & 1.0000 & 0.2749 & 0.6140 & 0.2632 & 1.0000 & 0.3918\\
Lead & 0.6491 & 0.4035 & 0.2749 & 1.0000 & 0.5906 & 0.3099 & 0.3918 & 1.0000\\
\bottomrule
\end{tabular}}
\end{table}

>>>>

\caption{\label{tab:unnamed-chunk-4}Descriptive statistics of simulated scores for qualification and final rounds}
\centering
\begin{tabular}[t]{lrrrrrrrr}
\toprule
round & min & Q1 & median & Q3 & max & mean & sd & n\\
\midrule
Qualification & 1 & 240 & 684 & 1638 & 8000 & 1158.84 & 1273.48 & 200000\\
Final & 1 & 24 & 60 & 126 & 512 & 91.20 & 91.11 & 80000\\
\bottomrule
\end{tabular}
\end{table}

@@

In this section, we discuss the results of our simulations described in
Section \ref{data-and-methods}. We first look at the chances of
advancing to the final round for a qualifier, given that 1) they finish
first in any of the three disciplines, and 2) they win the first event
(which happens to be speed climbing in reality). Our simulation study
shows that a climber is almost guaranteed to make the final round if
they win at least one of the three climbing concentrations (99.51\%, see
Table) or if they win the opening event (99.48\%, see Table). After
winning the first event, a climber is also more likely to finish first
overall (30\%, see Table) than any other positions in the overall
qualification rankings. Therefore, this product of ranks scoring format
highly rewards climbers who can get off to a strong start, which is a
major strategy climbing athletes should take note of.

In addition, the average score for qualification positions 1 to 8 are
displayed in Table X. We notice that on average, the minimum score that
one should aim for in order to move on to the final round is about 434
(for 8th rank).

@@

\caption{\label{tab:unnamed-chunk-6}title}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{rrrrrrrr}
\toprule
\multicolumn{4}{c}{Win Any} & \multicolumn{4}{c}{Win First} \\
\cmidrule(l{3pt}r{3pt}){1-4} \cmidrule(l{3pt}r{3pt}){5-8}
Rank & Count & Probability & Cumulative & Rank & Count & Probability & Cumulative\\
\midrule
1 & 7890 & 0.2762 & 0.2762 & 1 & 2999 & 0.2999 & 0.2999\\
2 & 5943 & 0.2080 & 0.4842 & 2 & 1963 & 0.1963 & 0.4962\\
3 & 4644 & 0.1626 & 0.6467 & 3 & 1559 & 0.1559 & 0.6521\\
4 & 3651 & 0.1278 & 0.7745 & 4 & 1269 & 0.1269 & 0.7790\\
5 & 2766 & 0.0968 & 0.8714 & 5 & 957 & 0.0957 & 0.8747\\
\addlinespace
6 & 1960 & 0.0686 & 0.9400 & 6 & 686 & 0.0686 & 0.9433\\
7 & 1118 & 0.0391 & 0.9791 & 7 & 363 & 0.0363 & 0.9796\\
8 & 448 & 0.0157 & 0.9948 & 8 & 155 & 0.0155 & 0.9951\\
9 & 127 & 0.0044 & 0.9992 & 9 & 42 & 0.0042 & 0.9993\\
10 & 19 & 0.0007 & 0.9999 & 10 & 6 & 0.0006 & 0.9999\\
\addlinespace
11 & 3 & 0.0001 & 1.0000 & 11 & 1 & 0.0001 & 1.0000\\
\bottomrule
\end{tabular}}
\end{table}

{\centering \includegraphics{draft_files/figure-latex/unnamed-chunk-7-1}

\caption{Probability of finishing at every rank given}\label{fig:unnamed-chunk-7}
\end{figure}

\caption{\label{tab:unnamed-chunk-8}The average scores for the top 10 qualification ranks according to our simulations. A climber will secure a finalist spot if they finish in the top 8.}
\centering
\begin{tabular}[t]{rr}
\toprule
Rank & Average score\\
\midrule
1 & 36.0187\\
2 & 73.6111\\
3 & 115.3954\\
4 & 162.2263\\
5 & 216.0041\\
\addlinespace
6 & 278.1649\\
7 & 350.3272\\
8 & 434.5932\\
9 & 532.1383\\
10 & 642.3298\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-9}title}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{rrrrrrrr}
\toprule
\multicolumn{4}{c}{Win Any} & \multicolumn{4}{c}{Win First} \\
\cmidrule(l{3pt}r{3pt}){1-4} \cmidrule(l{3pt}r{3pt}){5-8}
Rank & Count & Probability & Cumulative & Rank & Count & Probability & Cumulative\\
\midrule
1 & 9277 & 0.3512 & 0.3512 & 1 & 4295 & 0.4295 & 0.4295\\
2 & 7409 & 0.2805 & 0.6317 & 2 & 2505 & 0.2505 & 0.6800\\
3 & 5257 & 0.1990 & 0.8308 & 3 & 1702 & 0.1702 & 0.8502\\
4 & 3078 & 0.1165 & 0.9473 & 4 & 1020 & 0.1020 & 0.9522\\
5 & 1187 & 0.0449 & 0.9922 & 5 & 393 & 0.0393 & 0.9915\\
\addlinespace
6 & 198 & 0.0075 & 0.9997 & 6 & 83 & 0.0083 & 0.9998\\
7 & 7 & 0.0003 & 1.0000 & 7 & 2 & 0.0002 & 1.0000\\
\bottomrule
\end{tabular}}
\end{table}

{\centering \includegraphics{draft_files/figure-latex/unnamed-chunk-10-1}

\caption{Probability of finishing at every rank given}\label{fig:unnamed-chunk-10}
\end{figure}

@@

\caption{\label{tab:unnamed-chunk-11}The average scores for all final ranks according to our simulations. Ranks 1, 2, and 3 are table positions that guarantee medalist status for climbers.}
\centering
\begin{tabular}[t]{rr}
\toprule
Rank & Average score\\
\midrule
1 & 9.6687\\
2 & 20.1844\\
3 & 33.3658\\
4 & 50.5734\\
5 & 75.2499\\
\addlinespace
6 & 110.7070\\
7 & 164.8258\\
8 & 265.0198\\
\bottomrule
\end{tabular}
\end{table}

@@

{\centering \includegraphics{draft_files/figure-latex/unnamed-chunk-13-1}

@@

\caption{Kendall's rank correlations - 2018 World Championship, Men's and Women's Qualifications}\label{fig:unnamed-chunk-13}
\end{figure}

@@

{\centering \includegraphics{draft_files/figure-latex/unnamed-chunk-16-1}

@@

\caption{This figure illustrates the changes to the final rankings of the 2018 Youth Olympics Men's and Women's Finals when we leave out one climber. For each gender competition, each panel represents the rank of the drop-out athlete, with 0 being the original final results. Each case with a change in rank orderings is highlighted by a black panel border, and any player with a rank change is represented by a red-filled bar}\label{fig:unnamed-chunk-16}
\end{figure}

@@

\caption{\label{tab:unnamed-chunk-18}This table shows Kendall's rank correlation coefficients between the overall and individual discipline ranks for men's and women's sport climbing qualifications at the 2018 Asian Games}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lrrrrrrrr}
\toprule
\multicolumn{1}{c}{} & \multicolumn{4}{c}{Men} & \multicolumn{4}{c}{Women} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9}
  & Overall & Speed & Bouldering & Lead & Overall & Speed & Bouldering & Lead\\
\midrule
Overall & 1.0000 & 0.5731 & 0.6760 & 0.6126 & 1.0000 & 0.5474 & 0.6878 & 0.7053\\
Speed & 0.5731 & 1.0000 & 0.3022 & 0.2174 & 0.5474 & 1.0000 & 0.2540 & 0.2947\\
Bouldering & 0.6760 & 0.3022 & 1.0000 & 0.6203 & 0.6878 & 0.2540 & 1.0000 & 0.6878\\
Lead & 0.6126 & 0.2174 & 0.6203 & 1.0000 & 0.7053 & 0.2947 & 0.6878 & 1.0000\\
\bottomrule
\end{tabular}}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-19}This table shows Kendall's rank correlation coefficients between the overall and individual discipline ranks for men's and women's sport climbing qualifications at the 2019 World Championships}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lrrrrrrrr}
\toprule
\multicolumn{1}{c}{} & \multicolumn{4}{c}{Men} & \multicolumn{4}{c}{Women} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9}
  & Overall & Speed & Bouldering & Lead & Overall & Speed & Bouldering & Lead\\
\midrule
Overall & 1.0000 & 0.2632 & 0.3684 & 0.3474 & 1.0000 & 0.2316 & 0.5013 & 0.2526\\
Speed & 0.2632 & 1.0000 & -0.0947 & -0.3263 & 0.2316 & 1.0000 & 0.0686 & -0.4526\\
Bouldering & 0.3684 & -0.0947 & 1.0000 & 0.2000 & 0.5013 & 0.0686 & 1.0000 & 0.2902\\
Lead & 0.3474 & -0.3263 & 0.2000 & 1.0000 & 0.2526 & -0.4526 & 0.2902 & 1.0000\\
\bottomrule
\end{tabular}}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-20}This table shows Kendall's rank correlation coefficients between the overall and individual discipline ranks for men's and women's sport climbing qualifications at the 2020 European Championship}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lrrrrrrrr}
\toprule
\multicolumn{1}{c}{} & \multicolumn{4}{c}{Men} & \multicolumn{4}{c}{Women} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9}
  & Overall & Speed & Bouldering & Lead & Overall & Speed & Bouldering & Lead\\
\midrule
Overall & 1.0000 & 0.0947 & 0.3810 & 0.2632 & 1.0000 & 0.1847 & 0.5358 & 0.5368\\
Speed & 0.0947 & 1.0000 & -0.1587 & -0.4316 & 0.1847 & 1.0000 & -0.1915 & -0.0897\\
Bouldering & 0.3810 & -0.1587 & 1.0000 & 0.2751 & 0.5358 & -0.1915 & 1.0000 & 0.5040\\
Lead & 0.2632 & -0.4316 & 0.2751 & 1.0000 & 0.5368 & -0.0897 & 0.5040 & 1.0000\\
\bottomrule
\end{tabular}}
\end{table}

@@

\caption{\label{tab:unnamed-chunk-21}This table shows Kendall's rank correlation coefficients between the overall and individual discipline ranks for men's and women's sport climbing qualifications at the 2020 Pan American Championship}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lrrrrrrrr}
\toprule
\multicolumn{1}{c}{} & \multicolumn{4}{c}{Men} & \multicolumn{4}{c}{Women} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9}
  & Overall & Speed & Bouldering & Lead & Overall & Speed & Bouldering & Lead\\
\midrule
Overall & 1.0000 & 0.5906 & 0.5556 & 0.6491 & 1.0000 & 0.5789 & 0.6140 & 0.5906\\
Speed & 0.5906 & 1.0000 & 0.2164 & 0.4035 & 0.5789 & 1.0000 & 0.2632 & 0.3099\\
Bouldering & 0.5556 & 0.2164 & 1.0000 & 0.2749 & 0.6140 & 0.2632 & 1.0000 & 0.3918\\
Lead & 0.6491 & 0.4035 & 0.2749 & 1.0000 & 0.5906 & 0.3099 & 0.3918 & 1.0000\\
\bottomrule
\end{tabular}}
\end{table}
